Synthetic network and data generation using GeneNetWeaver(GNW)

### 2016-02-28 code/Rmd/synNetGen.Rmd
Minor changes

## Load required libraries
library(synapseClient)
library(ggplot2)
library(reshape2)
library(data.table)
library(dplyr)
library(stringr)
library(limma)
library(knitr)
library(Biobase)
library(GEOquery)
library(RColorBrewer)
library(gplots)
library(WGCNA)
library(psych)
library(edgeR)
library(biomaRt)
library(ggplot2)
library(WGCNA)

## Needs the dev branch
library(rGithubClient)

>>>>

## Load required libraries
library(synapseClient)
library(data.table)
library(dplyr)
library(stringr)
library(knitr)

## Needs the dev branch
library(githubr)
